Differential invariant signatures for planar Lie group transformations of images

### 2020-11-09 paper/newpaper.tex
Updates to conformal

Including $J_2$ in addition provides a 4-dimensional signature set, but does not increase the codimension of the set of bad images.

@@

The conformal diffeomorphisms provides a particularly nice example of the moving frame method. Define $\psi^{-1}(\bar{z}) = a_0 + a_1 \bar{z} + a_2 \bar{z}^2 + \dots = z$ where $z=x+iy$ and $a_i\in \mathbb{C}$. (Clearly $a_0$ is simply the translation to the origin). Note that at derivative order $n$ two real group parameters enter: $Re(a_n)$ and $Im(a_n)$. There are $n+1$ independent derivatives of $f$ of order $n$, so there must be at least $n-1$ independent invariants at each order. Working in real and imaginary coordinates, $f(x,y) = g(\bar{x}, \bar{y})$ and the moving frame computation proceeds as follows:

At first order, $(a_1 + i b_i) (\bar{x} + i \bar{y}) = x + i y$. Then:
\begin{align}
g_{\bar{x}} &= f_x x_{\bar{x}} + f_y y_{\bar{x}} \\
&= a_1 f_x + b_1 f_y \\
g_{\bar{y}} &= f_x x_{\bar{y}} + f_y y_{\bar{y}} \\
&= - b_1 f_x + 1_1 f_y 
\end{align}

Choosing $g_{\bar{x}} = 1$ and $\g_{\bar{y}} = 0$ gives $a_1 = f_x / (f_x^2 + f_y^2), \:\: b_1 = f_y / (f_x^2 + f_y^2)$. The second order computations give three equations, setting $g_{\bar{x} \bar{x}} = \g_{\bar{x} \bar{y}} = 0$ means that $g_{\bar{y} \bar{y}}$ gives the sole second-order invariant $f_{xx} + f_{yy} / (f_x^2 + f_y^2)$, which we also saw for the M\"bius group.

At third order there are two more invariants, ***

>>>>

Including $J_2$ in addition provides a 4-dimensional signature set, but does not increase the codimension of the set of bad images.%

@@

The conformal diffeomorphisms provides a particularly nice example of the
moving frame method. Letting $z = x + iy$, let $\bar{z} = \psi(z)$ be a conformal
mapping. It's convenient to work with the inverse transformation, so let
\begin{equation*}
    z = \psi^{-1}(\bar{z}) = c_0 + c_1 \bar{z} + c_2 \bar{z}^2 +
    c_3\bar{z}^3 + \cdots
\end{equation*}
where $c_i = a_i + ib_i \in \mathbb{C}$.  Because the group is infinite
dimensional, we need to work on the prolongation of $\psi$ to the jet space
$J^\infty = \{x, y, f, f_x, f_y, \ldots\}$ including all of its
derivatives. To make $\psi$ into a moving frame, we specify the
cross-section and solve for parameters in stages. We begin with $\bar{x} =
\bar{y} = 0$. This yeilds $c_0 = z$. To find $c_1 = a_1 + i b_1$ we need
two constraints. Differentiating $f(x, y) = \bar{f}(\bar{x}, \bar{y})$ and
substituting in our existing cross section constraints $\bar{x} = \bar{y} = 0$ gives
\begin{align*}
    \bar{f}_{\bar{x}} = f_x x_{\bar{x}} + f_y y_{\bar{x}} &= a_1 f_x + b_1
    f_y, \\
    \bar{f}_{\bar{y}} = f_x x_{\bar{y}} + f_y y_{\bar{y}} &= -b_1 f_x + a_1
    f_y. 
\end{align*}
Note that $\bar{x} = \bar{y} = 0$ removes all higher order derivatives from
the cross section equation. Adding two extra constraints to the cross
section, $\bar{f}_{\bar{x}} = 1, \bar{f}_{\bar{y}} = 0$, this system is readily
solved to give 
\begin{equation*}
    \begin{aligned}
        a_1 &= f_x / (f_x^2 + f_y^2), &  b_1 &= f_y / (f_x^2 + f_y^2).
    \end{aligned}
\end{equation*}
We then repeat the process, this time using the second derivative
computations. This time, there are two new parameters, $a_2, b_2$, to solve
for, but there are three derivatives. We use the cross section equations
$\bar{f}_{\bar{x}\bar{x}} = 0, \bar{f}_{\bar{x}\bar{y}} = 0$ to solve for
$a_2$ and $b_2$, the remaining derivative $\bar{f}_{\bar{y}\bar{y}}$ is then the
sole second order invariant, which we also saw for the M\"obius group: 
\begin{equation*}
    \bar{f}_{\bar{y}\bar{y}} = \frac{f_{xx} + f_{yy}}{f_x^2 + f_y^2}.
\end{equation*}
Continuing in this way, at derivative order $n$ two real group parameters
enter: $a_n$ and $b_n$. There are $n+1$ independent derivatives of $f$ of
order $n$, so there must be $n-1$ new independent invariants at each order.

At third order there are two more invariants, using the constraints
$\bar{f}_{\bar{x}\bar{x}\bar{x}} = 0, \bar{f}_{\bar{x}\bar{x}\bar{y}} = 0$,
the remaining derivatives are invariant:
\begin{align*}
    \bar{f}_{\bar{x}\bar{y}\bar{y}} &= \frac{f_y^3f_{yyy} + f_x^2f_yf_{yyy}
            -2f_y^2f_{yy}^2 - 2f_{xx}f_y^2f_{yy} -
            4f_xf_{xy}f_yf_{yy} - 2f_x^2 f_{xx}f_{yy} + f_{xxy}f_y^3 +
            f_x^2 f_{xxy}f_y - 4 f_x f_{xy} f_{xx} f_y + f_x^3 f_{xxx} -
        2f_x^2 f_{xx}^2 + f_x^3 f_{xyy}}{(f_x^2 + f_y^2)^3} \\
        \bar{f}_{\bar{y}\bar{y}\bar{y}} &= \frac{f_xf_y^2f_{yyy} +
        f_x^3f_{yyy} - 2f_x f_y f_{yy}^2 + 2f_{xy}f_y^2f_{yy} -
    2f_x^2f_{xy}f_{yy} - f_{xxx}f_y^3 - f_{xyy}f_y^3 + f_xf_{xxy}f_y^2 +
2f_{xy}f_{xx}f_y^2 - f_x^2 f_{xxx} f_y + 2f_xf_{xx}^2 f_y - f_x^2 f_{xyy}
f_y + f_x^3 f_{xxy} - 2f_x^2 f_{xy} f_{xx} }{(f_x^2 + f_y^2)^3 }
\end{align*}
